---
title: "hw-02"
author: "Andrew Thomson (S2138243)"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(lubridate)
edibnb <- read_csv("data/edibnb.csv")
council <- read_csv("data/council_assessments.csv")
```


### Exercise 1

```{r hw2-ex1}
edibnb %>%
select(id, review_scores_rating, number_of_reviews) %>%
filter(review_scores_rating == "100") %>%
  arrange(desc(number_of_reviews)) %>%
  slice(1)

```


ID: 860170

### Exercise 2

```{r hw2-ex2}
edibnb %>%
select(price, neighbourhood, accommodates) %>%
filter(neighbourhood == "Southside",
       accommodates >= "4") %>%
summarise(minimum_price = min(price),
          maximum_price = max(price),
          average_price = mean(price))

```
minimum price for an AirBnB = £10
maximum price for an AirBnB = £784
average price for an AirBnb = £143.19


### Exercise 3

```{r hw2-ex3}
edibnb %>%
mutate(number_of_bathrooms = ceiling(bathrooms)) %>%
select(number_of_bathrooms, bedrooms) %>%
filter(number_of_bathrooms > bedrooms) %>%
count(no_rows = TRUE)

```

963 have more bathrooms than bedrooms

### Exercise 4

```{r hw2-ex4}
right_join(edibnb, council) %>%
select(neighbourhood, rating) %>%
ggplot(mapping = aes(x = rating)) +
  geom_bar() +
facet_wrap(~neighbourhood)
```
The Leith area is assessed the most compared to all other areas.
The Tollcross area is assessed the least compared to all other areas.
The graphs show that some areas of Edinburgh get visited and seen to more regular so there for the council are not targeting all areas of Edinburgh the same 
### Exercise 5

```{r hw2-ex5}

```


_Remove this text, and add your answer for Exercise 5 here._

